Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2015-05-24 structured.tex
2015.05.18 (Alex) Gone through spelling correction. Added minimal biography text for authors. Some more re-wording on the connection sentences in the discussion section. Moving table and plots to improve overall typesetting in the structured section.

This section offers description and analysis of algorithms proposed
to address the topology mismatch problem in structured \p\ networks. 
The categorization of the approaches is based on how different
levels of proximity information is gathered as well as  
the way peer routing tables are maintained and used in an effort to make 
overlays as efficient as possible in terms of hops traversed.
%%AD what does it really mean this below???
%%VM it means that this split into i) geographic layout, ii) proximity routing
%%   and iii) proximity neighbour selection types of algorithms are terms
%%   coined in those papers
Our categirization is based on previous work 
found in~\cite{CDHR2002,CDCR2002,RSS2002}.

@@

\emph{Mithos}~\cite{WR2003} ensures that neighbouring nodes in the overlay are
close also in terms of the underlying layer by integrating proximity layout
and proximity routing overlay optimizations.

@@

$J$ is then assigned a synthetic \emph{ID} that
represents the state of minimum distance from its close-by $2$-$d$ neighbourhood as
this was discovered during the aforementioned phase. % iterative selection phase.
The benefit of adopting synthetic coordinates is that distance computations
among nodes can be done in the \emph{ID} space without requiring physical
measurements. 
Mithos proceeds then to designate $J$'s closest neighbours as 
previous steps do not reveal with certainty which these nodes are.
%%
Using Mithos \emph{quadrant-based} mechanism,
$J$  divides the $2$--$d$ space of neighbours in four regions and 
subsequently, establishes a link 
to the closest neighbor in each quadrant of the plane. 
% With peer $J$ dividing the plane into four regions,
% the \emph{quadrant-based} mechanism Mithos employs, suggests that the node
% establishes a link to the closest neighbor in each quadrant of the plane. 
%%
It does so, by starting from a known node in the neighbourhood
and scanning towards all quadrant borders ~\cite{KK2000,R2002}.

@@

%The protocol is based on four definitions.
%\begin{enumerate}
% \item The amplitude of all possible measured RTTs is divided into intervals.
%  Each node measures its distance to its parent and is assigned a label $L_i$
% where $i$ denotes the configurable RTT interval in which the measured distance
% falls into. A special kind of node, the root, is initially assigned the $L_1$
% label and maintains (as all $L_1$ nodes do) a list of other $L_1$ nodes in the
% overlay.
% \item Any node can have children with level lower than theirs, except an
%  $L_{max}$ node which can only have $L_{max}$ level children and only in the
% case when its parent has reached its maximum degree.
% \item Each node is assigned a dot-formated address (e.g 1.3.4). Each octet
% ranges from
% $1$ to $d$, where $d$ is the maximum degree of the nodes. The assignment
% process
% is done by appending a unique octet to the address of each nodes parent, while
% root node is assigned address $1$.
% \item For any descendant node $Y$ of a node $X$, the measured distance among
%  each other, must always be less than the lower bound of the RTT interval
% denoted by $X$'s label.
%\end{enumerate}
%

@@

%%AD a better connection with the mismatch problem has to be made... 
%%		.. in the form of 1-2 lines (or short statements). 
%%
%% VM Added some extra lines and restructured the text
\emph{T2MC}'s~\cite{SLCGZ2008} objective is to diminish the redundant multiple
messages that may unnecessarily cross autonomous system (\emph{AS}) boundaries.
The latter represent links that are the costliest to ISPs and hence, 
mininizing topology mismatches  greatly affects pertinent operational expenditure.
%%
To achieve that, each node exploits the stable structure of
the Internet routers to help solve a clustering problem. 
The algorithm uses {\sl traceroute}-logs to detect inter-\emph{AS} boundaries 
and clusters peers to either nearby or 
far-away groups by applying a customized $k$-mean classification ($k=2$).
%%
When joining the network, the peer randomly picks an IP and uses
traceroute and selects the routers with
minimum and maximum latencies in the above {\sl traceroute} path 
as initial centroids for the ``nearby'' and ``far-away'' sets respectively.
Following an iterative procedure, the node comes up with the two sets 
demostrating minimum intra-set latency variance.
At this stage, routers in the ``far-away'' set are not considered critical.
%%
%%AD skipping the details???? JUST CHECK
% Skipping the details of the algorithm, it picks the routers with
% minimum and maximum latencies in the above traceroute path as initial centroids
% for the ``near'' and ``remote'' sets respectively and after some iterations it
% ends up with two sets having the minimum intra-set latency variance. 
%%
% The router from the ``far-away'' set that presents the closest distance 
% from the peer in terms of hops, is designated as beacon.
% Any node portaying dinstance longer that the above is classified 
% as 
% 
% to the peer, in terms of hops, is designated as a beacon.
% Any node whose distance is measured to be longer that the distance 
% between 
% 
% The router with the minimum hops in the ``remote'' set is set up as the hop
% threshold and anything above that is classified as the ``remote'' router cluster
% for that peer. 
% Similarly, 
In contrast, the router from the ``near'' set
having the maximum number of hops 
from the just-joining peer is key as it denotes an edge--gateway. 
Peers that share the same edge--gateway or other members in the ``nearby'' 
router cluster are considered intra-\emph{AS} neighbors.
%%AD the final phrase for this is missing! So what??? What is achieved? 1 sentence.

Even though {\sl traceroute}
provides detailed information about the network structure, 
its extensive use may create overhead on the overall network structure. 
In this respect, administrators frequently
disable {\sl traceroute} support on their routers this 
undoubtly affects \emph{T2MC}'s operation.
%%
Although overall experimental results have been encouraging, 
\emph{T2MC} is considered rather coarse-grained as it only
classifies neighbours into two groups \cite{QLZG2009}.
%
%T2MC \cite{SLCGZ2008} uses trace-route logs to detect different autonomous
%systems and cluster close by peers, thus reducing redundant traffic that crosses
%autonomous system boundaries. T2MC uses a customized k-mean classification
%algorithm with $k=2$ to perform the classification, and exploits the stable
%structure of the Internet routers to guide clustering. The peer chooses the
%minimum and maximum Latency results from the trace-route to initialize the
%centroids of two sets. Then the peer calculates, for all hops along its
%trace-routed path, the peer calculates the absolute distance to these centroids
%of both sets and assigns the routers to that centroid with which it has the
%smaller absolute distance. After that, the mean and variance values are
%calculated and if the variance is larger than a predefined threshold then the
%algorithm sets the two latency mean values as new centroids for the two sets and
%loops again. Ultimately peer will end up with two sets having the minimum
%intra-set variance. The peer, then, chooses the router from the second set with
%the minimum hops attribute and sets it as a threshold. The selected router and
%all others whose hops attribute is larger than the threshold are classified as
%\emph{remote} router cluster. The remaining are classified as \emph{near}. From
%the near class, the peer chooses the one with maximum hops attribute as its edge
%router, and registers it along with all near clusters into the DHT of the
%\p\ overlay. As new peers join the network, those that share the same edge
%router or any of the members of the near router clusters, would form a close
%peer cluster. As Edge routers can provide more valuable information than other
%members of the near set, T2MC was designed to prioritize interaction of peers
%and edge gateways.
%
%
% TODO: SOME DISCUSSION
%
%The use of Trace-route as a tool for implementing the distance measuring
%infrastructure raise concerns about its efficiency and scalability. Being,
%primarily, a network diagnostic utility,
% Even though trace-route provides detailed information about the network
% structure, its excessive use creates additional overhead that stresses further
% the overall network infrastructure. This forces network administrators to
% disable its support from the routers they manage, thus jeopardizing the
% effectiveness of the T2MC algorithm.
%
\emph{T2MC} fares as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% The efficiency of choosing close by peers is very good and reported almost
% 65\% better than that of GNP (and thus generally of static landmarking as a
% whole)
high &
% trace-route is a very heavy tool and thus incurs excessive burden to the
% network resources.
high &
% Trace-route is categorized as too heavy-weighted and intrusive for use in a
% larger scale system \cite{RKHS2002}. Additionally, disabling
% ICMP is a common administrative policy for edge sites to enforce security,
% while dumping BGP routing tables\cite{krishnamurthy_bgpclust_2000} is not
% directly available to the application layer.
low
\end{tabular}
}
\end{center}

@@

Unfortunatelly the overlay maintenance cost is somewhat higher than
\emph{Chord} as additional heart-beat messages are required for
connection verification for the entries of the proximity list. 
Fortunately, such entries represent nodes 
already close-by so the additional cost is kept to a minimum.
However, \emph{PChord} has been reported to exhibit slow convergence speed 
and inefficiency in high-churn environments~\cite{DK2006}.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% VM:
%% Removed this whole chuck since most of it sounded like
%% repetition of the rest of the text below after all.
%% Please review and remove if you aggree.
%%
% Passing through proximity links, in the underlying network, 
% means reduced routing cost. 
% Moreover, if the number of entries in the proximity list is the same
% as the number of network partitions, 
% \emph{PChord} prevents hops from jumping in and
% out of network partitions the current node belongs to.
% On one hand, 
% \emph{PChord}’s advantageous  points are that 
% its routing attains fewer overlay hops, 
% it crosses network partition(s) only once by following proximity links
% and it maintains the light-weight maintenance cost of \emph{Chord}.
% On the other, \emph{PChord} exhibits slow convergence speed 
% and inefficiency in high-churn environments~\cite{DK2006}.
% %%AD rephrased what is below as above... 
% % \emph{PChord}’s advantages include the fact 
% % that the main routing optimizations are of
% % less overlay hops, following proximity links and crossing the same network
% % partition only once along a routing path while in the same time keeping Chord's
% % light-weight maintenance cost. 
% % On the other hand, it exhibits slow convergence
% 	% speed and inefficiency in a high churn environment \cite{DK2006}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\emph{PChord} qualitatively behaves as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Small decrease in needed overlay hops per object publishing but rigid in
% high churn environments.
medium &
% The are heartbeat mechanism for both finger table and proximity list adds a
% burden to the network by default. But the overall overhead is decreased as
% the proximity list becomes longer.
medium &
% Improvement of routing is achieved with more object pointers helping to
% shorten the routing path of object querying. When the distance of query source
% to target is far away both Chord and PChord achieve the average hop number to
% not increase.
medium
\end{tabular}
}
\end{center}

@@

Individual elements are uniquely mapped to the identifier--space,
allowing logarithmic lookup operations with high 
probability on \emph{Chord}. 
To this end, 
a node can obtain its \emph{DHT} key and its region key, 
in a fully distributed manner, just by applying a consistent hash function. 
The node can then communicate with the region's
master node called \emph{Cluster Node (CN)} which 
is responsible for clustering 
the nodes belonging in the same sector or 
region with that of the node at hand. 
%%
The node registers to its corresponding region  and publishes
its information, through the special peer \emph{CN};
the peer can also ask \emph{CN} for other
nodes that have previously joined the region to enhance 
the peer's neighbor set for future routing table optimization.
%
If no other nodes are found within the region, 
the search is expanded to neighbouring regions.
%
%% VM rephrase the one bellow as above in a super compact form
%%AD the one below is not a parse-able sentence!!! What does it say???
%%%		restrict the length of your sentences to say at most 2.5 lines!
%Even in the case when no
%neighbor is detected in the current region, the search is expanded to adjacent
%regions and towards an upper layer identifier space until one is found or the
%first layer reached. Simulations suggest that the scheme has good convergence
%property of the delay distribution and good optimizing performance.
%
%
%%AD up to here the text in this second paragraph for Chord DHT remains 
%%%%%		... rather cryptic - does need work and better connection 
%%%%%		with the 1st paragraph...
%%
Even though scaling appeared promising, only limited 
simulations were carried out with configurations involving up to 2,048 nodes.
Moreover the approach assumes uniform node distribution which
is not always the case, especially in a synthetic coordinate system.
%%
\emph{Chord DHT} fares as follows in reference to the stated $3$ criteria:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
medium &
%
medium &
%
medium
\end{tabular}
}
\end{center}

@@

% within that group. The Cone topology can be visualised as another ring on top

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\emph{3D Overlay (3DO)}~\cite{AOS2014} seeks to address the 
network mismatch problem  for peers operating in mobile networks.
As its name suggests, the network logical space is 
a $3$--$d$ space and the used ``transient'' (continually changing) 
logical \emph{ID}s (\emph{LID}s) consist of $3$ axes, $x$, $y$ and $z$ 
in the form of a tuple;
each such axis value is represented by an $M$-bit identifier.
%%
A newlly-arriving peer broadcasts a join request using
an \emph{TTL}-based expanding ring search helping locate 
peers that are physically adjacent.
Responding peers send in 
their \emph{LID}s along with a list of their neighbors 
and their corresponding distances from those neightbors. 
%%
Once a joining peer receives the above responses,
it stores requisite information in its own routing table 
and so, it generates an undirected connected
graph of itself with both its $1$- and $2$-hop neighbours. 
%%
Starting off this graph and with the help of hop 
distances obtained from the underlying MANET,
the incoming peer builds a minimum spanning tree (MST)
with itself as the root node; 
in this MST, the nodes adjacent to the root become the
direct neighbors of the peer.
%%
Moreover, the entries of the initial routing table 
that do not correspond to above direct neighbors are
eliminated.

The above procedure ascertains that close peers on the
overlay are also adjacent at the physical layer. 
%%
At this stage, a peer can generate its \emph{LID}
that automatically places it in the $3$-$d$ network space.
Updates in the peer's connectivity infromation 
reflecting continual changes in the mobile network,
trigger updates on the composition of \emph{LID} itself.

@@

During the \emph{jumping phase}, the source node calculates the 
stretch change to all its direct neighbours and to the direct neighbours
of the first peer that was selected in the probing phase, as if
the jump has been performed. 
Using heuristics, the node determines if the stretch
reduction is sufficient to perform the actual jump; 
otherwise, it selects the second peer from the probing phase 
and repeats the computation. If again, the
threshold is not met, then no jump is ultimately carried out.

@@

Table~\ref{structured:table} offers a comparative view 
on how our surveyed approaches behave.
The topics of topology adaptation, landmarking and caching/replication
are not further elaborated as they have been discussed 
in Section~\ref{section:unstructured}.
In a similar fashion to Table~\ref{unstructured:table}, 
we outline key properties of each surveyed approach 
that helps diffferentiate techniques from competitors.
We also highlight pros and cons for all proposals discussed.

%%AD Connection???  to the groups???
In what follows, we place the surveyed structured \p2p-methods in 
the three categories mentioned above and which are formulated based 
on utilized proximity and geographic aspects.

@@

%% VM: I reworded the above as below.
This category consists of methods that try to map the overlay id space on to
the physical one, as depicted in Figure~\ref{figure:geographic-layout}.
Routing tables of involved peers, are adjusted and maintained by exploiting
proximity information that describes the overall (geographic) positioning of
the participants. This comes in contrast to proximity routing and proximity neighbour
selection (discussed later on) where decisions are taken based on and effecting
a peer's nearby environment.

\begin{figure}[ht]
\centering
  \includegraphics[scale=0.44]{img/pdf/geographic-layout.pdf}
\caption{Successive nodes in the overlay circle can be chosen to be from the
same or near autonomous systems (\emph{AS}).}
\label{figure:geographic-layout}
\end{figure}
%%
A number of the reviewed algorithms including 
\emph{Global Soft-State},
\emph{Mithos} and \emph{LAPTOP} resort to clustering close-by nodes in
order to reduce the network's average delay.
Landmark servers and \emph{RTT} measurements are two popular methods, which
can also be used in conjunction, to discover peers in physical proximity.
However, as already discussed, these
methods do not always yield reliable estimates for node positions over the
Internet. 
Landmark servers are not self-organizing and present maintenance
overhead. Moreover, to serve a structured \p--network with potentially 
tens of thousands or more 
% millions 
peers, multiple such servers are required to be distributed over the world, 
which is a difficult proposition per se.
\emph{RTT}s can measure the delay between peers, but their use constitutes a
greedy method that can result in sub-optimal overlay topologies;
the latter is especially true if nearby 
nodes happen to be connected through low bandwidth connections.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{structured-table}

\input{structured-plot}

>>>>

This section offers description and analysis of algorithms proposed
to address the topology mismatch problem in structured \p\ networks. 
The categorization of the approaches is based on how different
levels of proximity information is gathered as well as  
the way peer routing tables are maintained and used in an effort to make 
overlays as efficient as possible in terms of hops traversed.
%%AD what does it really mean this below???
%%VM it means that this split into i) geographic layout, ii) proximity routing
%%   and iii) proximity neighbor selection types of algorithms are terms
%%   coined in those papers
Our categorization is based on previous work 
found in~\cite{CDHR2002,CDCR2002,RSS2002}.

@@

\emph{Mithos}~\cite{WR2003} ensures that neighboring nodes in the overlay are
close also in terms of the underlying layer by integrating proximity layout
and proximity routing overlay optimizations.

@@

$J$ is then assigned a synthetic \emph{ID} that
represents the state of minimum distance from its close-by $2$-$d$ neighborhood as
this was discovered during the aforementioned phase. % iterative selection phase.
The benefit of adopting synthetic coordinates is that distance computations
among nodes can be done in the \emph{ID} space without requiring physical
measurements. 
Mithos proceeds then to designate $J$'s closest neighbors as 
previous steps do not reveal with certainty which these nodes are.
%%
Using Mithos \emph{quadrant-based} mechanism,
$J$  divides the $2$--$d$ space of neighbors in four regions and 
subsequently, establishes a link 
to the closest neighbor in each quadrant of the plane. 
% With peer $J$ dividing the plane into four regions,
% the \emph{quadrant-based} mechanism Mithos employs, suggests that the node
% establishes a link to the closest neighbor in each quadrant of the plane. 
%%
It does so, by starting from a known node in the neighborhood
and scanning towards all quadrant borders ~\cite{KK2000,R2002}.

@@

%The protocol is based on four definitions.
%\begin{enumerate}
% \item The amplitude of all possible measured RTTs is divided into intervals.
%  Each node measures its distance to its parent and is assigned a label $L_i$
% where $i$ denotes the configurable RTT interval in which the measured distance
% falls into. A special kind of node, the root, is initially assigned the $L_1$
% label and maintains (as all $L_1$ nodes do) a list of other $L_1$ nodes in the
% overlay.
% \item Any node can have children with level lower than theirs, except an
%  $L_{max}$ node which can only have $L_{max}$ level children and only in the
% case when its parent has reached its maximum degree.
% \item Each node is assigned a dot-formatted address (e.g 1.3.4). Each octet
% ranges from
% $1$ to $d$, where $d$ is the maximum degree of the nodes. The assignment
% process
% is done by appending a unique octet to the address of each nodes parent, while
% root node is assigned address $1$.
% \item For any descendant node $Y$ of a node $X$, the measured distance among
%  each other, must always be less than the lower bound of the RTT interval
% denoted by $X$'s label.
%\end{enumerate}
%

@@

%%AD a better connection with the mismatch problem has to be made... 
%%		.. in the form of 1-2 lines (or short statements). 
%%
%% VM Added some extra lines and restructured the text
\emph{T2MC}'s~\cite{SLCGZ2008} objective is to diminish the redundant multiple
messages that may unnecessarily cross autonomous system (\emph{AS}) boundaries.
The latter represent links that are the costliest to ISPs and hence, 
minimizing topology mismatches  greatly affects pertinent operational expenditure.
%%
To achieve that, each node exploits the stable structure of
the Internet routers to help solve a clustering problem. 
The algorithm uses {\sl traceroute}-logs to detect inter-\emph{AS} boundaries 
and clusters peers to either nearby or 
far-away groups by applying a customized $k$-mean classification ($k=2$).
%%
When joining the network, the peer randomly picks an IP and uses
traceroute and selects the routers with
minimum and maximum latencies in the above {\sl traceroute} path 
as initial centroids for the ``nearby'' and ``far-away'' sets respectively.
Following an iterative procedure, the node comes up with the two sets 
demonstrating minimum intra-set latency variance.
At this stage, routers in the ``far-away'' set are not considered critical.
%%
%%AD skipping the details???? JUST CHECK
% Skipping the details of the algorithm, it picks the routers with
% minimum and maximum latencies in the above traceroute path as initial centroids
% for the ``near'' and ``remote'' sets respectively and after some iterations it
% ends up with two sets having the minimum intra-set latency variance. 
%%
% The router from the ``far-away'' set that presents the closest distance 
% from the peer in terms of hops, is designated as beacon.
% Any node portraying distance longer that the above is classified 
% as 
% 
% to the peer, in terms of hops, is designated as a beacon.
% Any node whose distance is measured to be longer that the distance 
% between 
% 
% The router with the minimum hops in the ``remote'' set is set up as the hop
% threshold and anything above that is classified as the ``remote'' router cluster
% for that peer. 
% Similarly, 
In contrast, the router from the ``near'' set
having the maximum number of hops 
from the just-joining peer is key as it denotes an edge--gateway. 
Peers that share the same edge--gateway or other members in the ``nearby'' 
router cluster are considered intra-\emph{AS} neighbors.
%%AD the final phrase for this is missing! So what??? What is achieved? 1 sentence.

Even though {\sl traceroute}
provides detailed information about the network structure, 
its extensive use may create overhead on the overall network structure. 
In this respect, administrators frequently
disable {\sl traceroute} support on their routers this 
undoubtly affects \emph{T2MC}'s operation.
%%
Although overall experimental results have been encouraging, 
\emph{T2MC} is considered rather coarse-grained as it only
classifies neighbors into two groups \cite{QLZG2009}.
%
%T2MC \cite{SLCGZ2008} uses trace-route logs to detect different autonomous
%systems and cluster close by peers, thus reducing redundant traffic that crosses
%autonomous system boundaries. T2MC uses a customized k-mean classification
%algorithm with $k=2$ to perform the classification, and exploits the stable
%structure of the Internet routers to guide clustering. The peer chooses the
%minimum and maximum Latency results from the trace-route to initialize the
%centroids of two sets. Then the peer calculates, for all hops along its
%trace-routed path, the peer calculates the absolute distance to these centroids
%of both sets and assigns the routers to that centroid with which it has the
%smaller absolute distance. After that, the mean and variance values are
%calculated and if the variance is larger than a predefined threshold then the
%algorithm sets the two latency mean values as new centroids for the two sets and
%loops again. Ultimately peer will end up with two sets having the minimum
%intra-set variance. The peer, then, chooses the router from the second set with
%the minimum hops attribute and sets it as a threshold. The selected router and
%all others whose hops attribute is larger than the threshold are classified as
%\emph{remote} router cluster. The remaining are classified as \emph{near}. From
%the near class, the peer chooses the one with maximum hops attribute as its edge
%router, and registers it along with all near clusters into the DHT of the
%\p\ overlay. As new peers join the network, those that share the same edge
%router or any of the members of the near router clusters, would form a close
%peer cluster. As Edge routers can provide more valuable information than other
%members of the near set, T2MC was designed to prioritize interaction of peers
%and edge gateways.
%
%
% TODO: SOME DISCUSSION
%
%The use of Trace-route as a tool for implementing the distance measuring
%infrastructure raise concerns about its efficiency and scalability. Being,
%primarily, a network diagnostic utility,
% Even though trace-route provides detailed information about the network
% structure, its excessive use creates additional overhead that stresses further
% the overall network infrastructure. This forces network administrators to
% disable its support from the routers they manage, thus jeopardizing the
% effectiveness of the T2MC algorithm.
%
\emph{T2MC} fares as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% The efficiency of choosing close by peers is very good and reported almost
% 65\% better than that of GNP (and thus generally of static landmarking as a
% whole)
high &
% trace-route is a very heavy tool and thus incurs excessive burden to the
% network resources.
high &
% Trace-route is categorized as too heavy-weighted and intrusive for use in a
% larger scale system \cite{RKHS2002}. Additionally, disabling
% ICMP is a common administrative policy for edge sites to enforce security,
% while dumping BGP routing tables\cite{krishnamurthy_bgpclust_2000} is not
% directly available to the application layer.
low
\end{tabular}
}
\end{center}

@@

Unfortunately the overlay maintenance cost is somewhat higher than
\emph{Chord} as additional heart-beat messages are required for
connection verification for the entries of the proximity list. 
Fortunately, such entries represent nodes 
already close-by so the additional cost is kept to a minimum.
However, \emph{PChord} has been reported to exhibit slow convergence speed 
and inefficiency in high-churn environments~\cite{DK2006}.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% VM:
%% Removed this whole chuck since most of it sounded like
%% repetition of the rest of the text below after all.
%% Please review and remove if you agree.
%%
% Passing through proximity links, in the underlying network, 
% means reduced routing cost. 
% Moreover, if the number of entries in the proximity list is the same
% as the number of network partitions, 
% \emph{PChord} prevents hops from jumping in and
% out of network partitions the current node belongs to.
% On one hand, 
% \emph{PChord}’s advantageous  points are that 
% its routing attains fewer overlay hops, 
% it crosses network partition(s) only once by following proximity links
% and it maintains the light-weight maintenance cost of \emph{Chord}.
% On the other, \emph{PChord} exhibits slow convergence speed 
% and inefficiency in high-churn environments~\cite{DK2006}.
% %%AD rephrased what is below as above... 
% % \emph{PChord}’s advantages include the fact 
% % that the main routing optimizations are of
% % less overlay hops, following proximity links and crossing the same network
% % partition only once along a routing path while in the same time keeping Chord's
% % light-weight maintenance cost. 
% % On the other hand, it exhibits slow convergence
% 	% speed and inefficiency in a high churn environment \cite{DK2006}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\emph{PChord} qualitatively behaves as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Small decrease in needed overlay hops per object publishing but rigid in
% high churn environments.
medium &
% The are heartbeat mechanism for both finger table and proximity list adds a
% burden to the network by default. But the overall overhead is decreased as
% the proximity list becomes longer.
medium &
% Improvement of routing is achieved with more object pointers helping to
% shorten the routing path of object querying. When the distance of query source
% to target is far away both Chord and PChord achieve the average hop number to
% not increase.
medium
\end{tabular}
}
\end{center}

@@

Individual elements are uniquely mapped to the identifier--space,
allowing logarithmic lookup operations with high 
probability on \emph{Chord}. 
To this end, 
a node can obtain its \emph{DHT} key and its region key, 
in a fully distributed manner, just by applying a consistent hash function. 
The node can then communicate with the region's
master node called \emph{Cluster Node (CN)} which 
is responsible for clustering 
the nodes belonging in the same sector or 
region with that of the node at hand. 
%%
The node registers to its corresponding region  and publishes
its information, through the special peer \emph{CN};
the peer can also ask \emph{CN} for other
nodes that have previously joined the region to enhance 
the peer's neighbor set for future routing table optimization.
%
If no other nodes are found within the region, 
the search is expanded to neighboring regions.
%
%% VM rephrase the one bellow as above in a super compact form
%%AD the one below is not a parse-able sentence!!! What does it say???
%%%		restrict the length of your sentences to say at most 2.5 lines!
%Even in the case when no
%neighbor is detected in the current region, the search is expanded to adjacent
%regions and towards an upper layer identifier space until one is found or the
%first layer reached. Simulations suggest that the scheme has good convergence
%property of the delay distribution and good optimizing performance.
%
%
%%AD up to here the text in this second paragraph for Chord DHT remains 
%%%%%		... rather cryptic - does need work and better connection 
%%%%%		with the 1st paragraph...
%%
Even though scaling appeared promising, only limited 
simulations were carried out with configurations involving up to 2,048 nodes.
Moreover the approach assumes uniform node distribution which
is not always the case, especially in a synthetic coordinate system.
%%
\emph{Chord DHT} fares as follows in reference to the stated $3$ criteria:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
medium &
%
medium &
%
medium
\end{tabular}
}
\end{center}

@@

% within that group. The Cone topology can be visualized as another ring on top

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\emph{3D Overlay (3DO)}~\cite{AOS2014} seeks to address the 
network mismatch problem  for peers operating in mobile networks.
As its name suggests, the network logical space is 
a $3$--$d$ space and the used ``transient'' (continually changing) 
logical \emph{ID}s (\emph{LID}s) consist of $3$ axes, $x$, $y$ and $z$ 
in the form of a tuple;
each such axis value is represented by an $M$-bit identifier.
%%
A newly-arriving peer broadcasts a join request using
a \emph{TTL}-based expanding ring search helping locate 
peers that are physically adjacent.
Responding peers send in 
their \emph{LID}s along with a list of their neighbors 
and their corresponding distances from those neighbors. 
%%
Once a joining peer receives the above responses,
it stores requisite information in its own routing table 
and so, it generates an undirected connected
graph of itself with both its $1$- and $2$-hop neighbors. 
%%
Starting off this graph and with the help of hop 
distances obtained from the underlying MANET,
the incoming peer builds a minimum spanning tree (MST)
with itself as the root node; 
in this MST, the nodes adjacent to the root become the
direct neighbors of the peer.
%%
Moreover, the entries of the initial routing table 
that do not correspond to above direct neighbors are
eliminated.

The above procedure ascertains that close peers on the
overlay are also adjacent at the physical layer. 
%%
At this stage, a peer can generate its \emph{LID}
that automatically places it in the $3$-$d$ network space.
Updates in the peer's connectivity information 
reflecting continual changes in the mobile network,
trigger updates on the composition of \emph{LID} itself.

@@

During the \emph{jumping phase}, the source node calculates the 
stretch change to all its direct neighbors and to the direct neighbors
of the first peer that was selected in the probing phase, as if
the jump has been performed. 
Using heuristics, the node determines if the stretch
reduction is sufficient to perform the actual jump; 
otherwise, it selects the second peer from the probing phase 
and repeats the computation. If again, the
threshold is not met, then no jump is ultimately carried out.

@@

In what follows, we place the surveyed \emph{structured} \p-methods in 
the three above categories formulated based on 
utilized proximity and geographic aspects.
Table~\ref{structured:table} offers a comparative view
of the algorithms in a way reminiscent to that used in Table~\ref{unstructured:table}.
Table~\ref{structured:table} outlines key properties for all surveyed approach 
that helps differentiate and better position competing techniques.
Clearly, we do not further elaborate topics that we have included and discussed 
at length in Section~\ref{section:unstructured}; these aspects entail 
topology adaptation, landmarking, and caching/replication.
Finally, Figures~\ref{structured:plot:efficiency}, \ref{structured:plot:overhead}
and \ref{structured:plot:scalability} help with the pictorial comparison
of the algorithms' bahavior with respect to the three effectiveness
criteria we defined in subsection~\ref{background:motivation}.

@@

%% VM: I reworded the above as below.
This category consists of methods that try to map the overlay id space on to
the physical one, as depicted in Figure~\ref{figure:geographic-layout}.
Routing tables of involved peers, are adjusted and maintained by exploiting
proximity information that describes the overall (geographic) positioning of
the participants. This comes in contrast to proximity routing and proximity neighbor
selection (discussed later on) where decisions are taken based on and effecting
a peer's nearby environment.

\begin{figure}[ht]
\centering
  \includegraphics[scale=0.44]{img/pdf/geographic-layout.pdf}
\caption{Successive nodes in the overlay circle can be chosen to be from the
same or near autonomous systems (\emph{AS}).}
\label{figure:geographic-layout}
\end{figure}
%%
A number of the reviewed algorithms including 
\emph{Global Soft-State},
\emph{Mithos} and \emph{LAPTOP} resort to clustering close-by nodes in
order to reduce the network's average delay.
%%
\input{structured-table}
%%
\input{structured-plot}
%%
Landmark servers and \emph{RTT} measurements are two popular methods, which
can also be used in conjunction, to discover peers in physical proximity.
However, as already discussed, these
methods do not always yield reliable estimates for node positions over the
Internet. 
Landmark servers are not self-organizing and present maintenance
overhead. Moreover, to serve a structured \p--network with potentially 
tens of thousands or more 
% millions 
peers, multiple such servers are required to be distributed over the world, 
which is a difficult proposition per se.
\emph{RTT}s can measure the delay between peers, but their use constitutes a
greedy method that can result in sub-optimal overlay topologies;
the latter is especially true if nearby 
nodes happen to be connected through low bandwidth connections.

@@
